Co-citations in context

### 2019-06-13 cocit_r.tex
Minor revisions

\textcolor{blue}{Placement and relevance to be determined.  This paragraph is not yet well written... still working on it.} We described concerns with model misspecification at the outset in two general dimensions: the background dataset and sampling methodology for the random graph. The differences we found from prior research in which categories demonstrated the highest hit rates were caused both by differences in the background dataset and in our sampling methodology through differences in article z-score distributions. When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles. We thought it important to identify which of our methodological approaches might account    Our sampling approach includes several enhancements to prior work, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines.

>>>>

\textcolor{blue}{Placement and relevance to be determined.  This paragraph is not yet well written... still working on it.} We described concerns with model misspecification at the outset along two general dimensions: the background dataset and sampling methodology for the random graph. The differences we found from prior research in terms of which categories demonstrated the highest hit rates were caused both by using disciplinary datasets and our sampling methodology through the article z-score distributions. When z-scores are shifted downward using one algorithm versus another, for example, then the former algorithm can result in an increased percentage of HN articles. We thought it important to determine the extent to which each of our methodological differences contributed to our observations.  We found that z-scores of 28.6\% of the journal pairs changed signs with our sampling algorithm, for example, when computed with respect to the WoS dataset versus the immunology dataset.  In contrast, 2.8\% of z-scores changed signs in the WoS dataset depending on whether Uzzi et al.'s or our random model was used and x\% z-scores changed signs in the case of the immunology dataset. \textcolor{blue}{Need to insert data for the immunology dataset here also for an apples-to-apples comparison.} We conclude that the choice of background datasets is the source of a majority of differences we observed the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
